Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-06-26 automatica/paper.tex
make figures readable
Further proof for the settling time limit

In a SISO system, there are 2 values that typically define the response-time of the system (using a step response).
\begin{enumerate}
\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
\end{enumerate} 
In the case of first and second order systems (with ), the decay is governed by the equations 
\begin{align*}
&y_{decay}=
&\left\{
\begin{array}{cc}
e^{-|\omega| t}& 1^{st} order\\
e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
\end{align*}
where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
These equations become increasingly complicated for higher order systems. However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
\begin{theorem}
Given a set of eigenvalues for a discrete time modle of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
\begin{equation}
t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
\label{eq:set_time}
\end{equation}
where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
\end{theorem} 
\begin{proof}
Given a closed loop single output LTI system of order $n$ with dynamics
\begin{equation}
\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right. \Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right. : \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
\end{equation}
%
the output decay is a linear combination of the decay of eigenvalues or
eigenvalue pairs.  Hence the overall decay of the system is always smaller
than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining
percentage of the decay expressed.  reversing we have
$t=-\frac{ln(p)}{|\overline{\omega}|}=-\frac{ln(p)}{ln(|\overline{\lambda}|)}$. 
replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
\eqref{eq:set_time}
%
\qed
\end{proof}
%
We may now use this limit to express a constraint in terms of the
coefficients for our synthesis process.  Let
%
\begin{equation}
P=\prod_{i=0}^n (s-\lambda_i)=\sum_{j=0}^n c_js^j.
\end{equation}
%
We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
to $P'=\prod_{i=0}^n (s-\lambda_i')=\sum_{j=0}^n c_j's^j$ where $c_j'$ are
unknown.  However, if we replace for $\lambda_i$, we obtain
%
\begin{equation}
P'=\prod_{i=0}^n (s-\lambda_i')=\prod_{i=0}^n (s-\lambda_i\overline{\lambda})=\sum_{j=0}^n c_j\overline{\lambda}^{n-j}s^j
\end{equation}
%
where all members are known, we may now synthesise coefficients that ensure
the eigenvalues are smaller than a desired magnitue, thus ensuring that the
settling time is too.

@@

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (r) edge (gain.west);
  \path[->] (gain.east) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (C.west)
   (C.east) edge (switch1.west)
   (switch2) edge (q1.west);
  \path
   (q1.east) edge (ykeast)
   (ykeast) edge (o2east);
  \path       (uksouth) edge (bdwest);
  \path[->] (bdwest) edge (Bd.west);
  \path
   (Bd.east) edge (o1.west)
   (o1.east) edge (delay.west)
   (xdsouth) edge (adeast)
   (adeast) edge (Ad.east)
   (Ad.west) edge (adwest)
   (adwest) edge (o1.south)
   (o2.west) edge (Ld.east)
   (Ld.west) edge (ldwest)
   (ldwest) edge (o1.north)
   (delay.east) edge (Cd.west)
   (Cd.north) edge (o2.south)
   (o2east) edge (o2.east)
   (xdsouth) edge (fbsouth)
   (fbsouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
\end{figure*}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an Observed System}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally $\mat{A}_o=\mat{A}_d$, $\mat{B}_o=\mat{B}_d$ and $\mat{C}_o=\mat{C}_d$ for a given time discretization.
A controllable and observable system will have the following dynamics:
\begin{equation}
\tiny
\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
\end{equation}
In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
reachable form and the observer error dynamics in observable form. Let 
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form

\begin{align}
\label{eq:observer_LTI_cf}
\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_k
+\mat{B}_{tp} \vec{r}_k
+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\\
\vec{y}_k=&\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k\nonumber
\end{align}
\begin{align*}
\mat{A}_{tp}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
\mat{A}_{to}=&\mat{T}_o\left(\mat{A}_d-\mat{L}_d\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]&
\mat{B}_{to}=&\mat{T}_c\mat{B}_d\mat{K}_d\mat{T}_o^{-1}\\
\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
\mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
\mat{C}_t=&\mat{C}_d\mat{T}_c
\end{align*}

@@

When our observer is implemented using a finite precision controller, new
problems arise due to the FWL effects.  Let $\mat{A}_o$, $\mat{B}_o$ and
$\mat{C}_o$ be the dynamics represented in $\mathbb{R} \langle I , F, E
\rangle$, and $\mat{A}_e=\mat{A}_d-\mat{A}_o$,
$\mat{B}_e=\mat{B}_d-\mat{B}_o$, and $\mat{C}_e=\mat{C}_d-\mat{C}_o$ their
corresponding errors.  Equation \eqref{eq:observer_LTI_cf} will become
%
\begin{align}
\tiny
\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
=&\tiny \left [\begin{array}{cc}\mat{A}_{tp}+\mat{B}_{eo}&\mat{B}_{to}\\ \mat{A}_{eo}&\mat{A}_{to}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_k
+\mat{B}_{tp} \vec{r}_k
+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\nonumber\\
\tiny\vec{y}_k=&\tiny\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
\begin{align*}
\mat{A}_{tp}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
\mat{A}_{to}=&\mat{T}_o\left(\mat{A}_o-\mat{L}_o\mat{C}_o\right)\mat{T}_o^{-1}\\
\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]&
\mat{B}_{to}=&\mat{T}_c\mat{B}_o\mat{K}_d\mat{T}_o^{-1}\\
\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_o\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_o\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
\mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
\mat{A}_{eo}=&\mat{T}_o\left(\mat{A}_e+\mat{L}_o\mat{C}_e\right)\mat{T}_o^{-1}\\
\mat{B}_{eo}=&\mat{T}_c\mat{B}_e\mat{K}_d\mat{T}_o^{-1}&
\mat{C}_t=&\mat{C}_d\mat{T}_c
\end{align*}

>>>>

In a SISO system, there are 2 values that typically define the response-time of the system (using a step response).
\begin{enumerate}
\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
\end{enumerate} 
In the case of first and second order systems (with ), the decay is governed by the equations 
\begin{align*}
&y_{decay}=
&\left\{
\begin{array}{cc}
e^{-|\omega| t}& 1^{st} order\\
e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
\end{align*}
where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
These equations become increasingly complicated for higher order systems. However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
\begin{theorem}
Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
\begin{equation}
t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
\label{eq:set_time}
\end{equation}
where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
\end{theorem} 
\begin{proof}
Given a closed loop single output LTI system of order $n$ with dynamics
\begin{equation}
\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right. \Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right. : \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
\label{eq:eigendynamics}
\end{equation}
%
the output decay is a linear combination of the decay of eigenvalues or
eigenvalue pairs.  
Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of the states $\vec{x}'_k$. We accelerate equation \eqref{eq:eigendynamics} to obtain
\begin{align}
%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^n \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
\end{align}
where the second  part of the equation corresponds to the upper diagonal terms of the Jordan blocks. We also have $|\lambda_i^k|\leq |\overline{\omega}^k|$,hence
\begin{align}
|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
\end{align}
Since we are synthesising the eigenvalues, rather than solve this formula for complex Jordan Shapes, we will restrict our synthesiser to provide solutions with distinct eigenvalues (which is by far the most common case). Therefore the right hand terms dissappear and we end up with
\begin{align}
|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
\end{align}

Hence the overall decay of the system is always smaller
than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining
percentage of the decay expressed.  reversing we have
$t=-\frac{ln(p)}{|\overline{\omega}|}=-\frac{ln(p)}{ln(|\overline{\lambda}|)}$. 
replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
\eqref{eq:set_time}
%
\qed
\end{proof}
%
We may now use this limit to express a constraint in terms of the
coefficients for our synthesis process.  Let
%
\begin{equation}
P=\prod_{i=0}^n (s-\lambda_i)=\sum_{j=0}^n c_js^j.
\end{equation}
%
We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
to $P'=\prod_{i=0}^n (s-\lambda_i')=\sum_{j=0}^n c_j's^j$ where $c_j'$ are
unknown.  However, if we replace for $\lambda_i$, we obtain
%
\begin{equation}
P'=\prod_{i=0}^n (s-\lambda_i')=\prod_{i=0}^n \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^n \frac{c_j}{\overline{\lambda}^{n-j}}s^j
\end{equation}
%
where all members are known, we may now synthesise coefficients that ensure
the eigenvalues are smaller than a desired magnitue, thus ensuring that the
settling time is too.

@@

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (r) edge (gain.west);
  \path[->] (gain.east) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (C.west)
   (C.east) edge (switch1.west)
   (switch2) edge (q1.west);
  \path
   (q1.east) edge (ykeast)
   (ykeast) edge (o2east);
  \path       (uksouth) edge (bdwest);
  \path[->] (bdwest) edge (Bd.west);
  \path
   (Bd.east) edge (o1.west)
   (o1.east) edge (delay.west)
   (xdsouth) edge (adeast)
   (adeast) edge (Ad.east)
   (Ad.west) edge (adwest)
   (adwest) edge (o1.south)
   (o2.west) edge (Ld.east)
   (Ld.west) edge (ldwest)
   (ldwest) edge (o1.north)
   (delay.east) edge (Cd.west)
   (Cd.north) edge (o2.south)
   (o2east) edge (o2.east)
   (xdsouth) edge (fbsouth)
   (fbsouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
\end{figure*}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an Observed System}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally $\mat{A}_o=\mat{A}_d$, $\mat{B}_o=\mat{B}_d$ and $\mat{C}_o=\mat{C}_d$ for a given time discretization.
A controllable and observable system will have the following dynamics:
\begin{align}
\tiny
\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
&\tiny=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k\nonumber\\
&\tiny+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
reachable form and the observer error dynamics in observable form. Let 
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form

\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_k
+\mat{B}_{tp} \vec{r}_k
+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\nonumber\\
\vec{y}_k=&\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
\begin{align*}
\mat{A}_{tp}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
\mat{A}_{to}=&\mat{T}_o\left(\mat{A}_d-\mat{L}_d\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]&
\mat{B}_{to}=&\mat{T}_c\mat{B}_d\mat{K}_d\mat{T}_o^{-1}\\
\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
\mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
\mat{C}_t=&\mat{C}_d\mat{T}_c
\end{align*}

@@

When our observer is implemented using a finite precision controller, new
problems arise due to the FWL effects.  Let $\mat{A}_o$, $\mat{B}_o$ and
$\mat{C}_o$ be the dynamics represented in $\mathbb{R} \langle I , F, E
\rangle$, and $\mat{A}_e=\mat{A}_d-\mat{A}_o$,
$\mat{B}_e=\mat{B}_d-\mat{B}_o$, and $\mat{C}_e=\mat{C}_d-\mat{C}_o$ their
corresponding errors.  Equation \eqref{eq:observer_LTI_cf} will become
%
\begin{align}
\tiny
\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
=&\tiny \left [\begin{array}{cc}\mat{A}_{tp}+\mat{B}_{eo}&\mat{B}_{to}\\ \mat{A}_{eo}&\mat{A}_{to}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_k
+\mat{B}_{tp} \vec{r}_k
+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\nonumber\\
\tiny\vec{y}_k=&\tiny\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
\begin{align*}
\mat{A}_{tp}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
\mat{A}_{to}=&\mat{T}_o\left(\mat{A}_o-\mat{L}_o\mat{C}_o\right)\mat{T}_o^{-1}\\
\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]&
\mat{B}_{to}=&\mat{T}_c\mat{B}_o\mat{K}_d\mat{T}_o^{-1}\\
\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_o\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_o&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
\mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
\mat{A}_{eo}=&\mat{T}_o\left(\mat{A}_e-\mat{L}_o\mat{C}_e\right)\mat{T}_o^{-1}\\
\mat{B}_{eo}=&\mat{T}_c\mat{B}_e\mat{K}_d\mat{T}_o^{-1}&
\mat{C}_t=&\mat{C}_d\mat{T}_c
\end{align*}
